### 2025-08-05 mixed-models.qmd
20250804 - clear memory

# From GAM Model: Players at Top of End-of-Season Depth Chart
pointsPerSeason_positionAge_newData$fantasyPoints_depthGAM <- predict(
  object = pointsPerSeasonDepth_gam,
  newdata = pointsPerSeason_positionAge_newData,
  newdata.guaranteed = TRUE,
  exclude = "s(player_idFactor,ageCentered20)"
)

@@

pointsPerSeason_positionAge_newData$player_idFactor <- factor(
  rep(model_levels[1], nrow(pointsPerSeason_positionAge_newData)), 
  levels = model_levels
)

modelPredictions_bayesian <- predict(
  object = bayesianMixedModelFit,
  newdata = pointsPerSeason_positionAge_newData,
  re_formula = NA,
  summary = TRUE
)

>>>>

# From GAM Model: Players at Top of End-of-Season Depth Chart
pointsPerSeason_positionAge_newData$fantasyPoints_depthGAM <- predict(
  object = pointsPerSeasonDepth_gam,
  newdata = pointsPerSeason_positionAge_newData,
  newdata.guaranteed = TRUE,
  exclude = "s(player_idFactor,ageCentered20)"
)
```

```{r}
#| label: generate-model-implied-predictions-fantasy-points-by-position-age-bayesian1

@@

pointsPerSeason_positionAge_newData$player_idFactor <- factor(
  rep(model_levels[1], nrow(pointsPerSeason_positionAge_newData)), 
  levels = model_levels
)
```

```{r}
#| label: clear-memory-bayesian1

gc()
```

```{r}
#| label: generate-model-implied-predictions-fantasy-points-by-position-age-bayesian2

modelPredictions_bayesian <- predict(
  object = bayesianMixedModelFit,
  newdata = pointsPerSeason_positionAge_newData,
  re_formula = NA,
  cores = num_cores
)
```

```{r}
#| label: clear-memory-bayesian2

gc()
```

```{r}
#| label: generate-model-implied-predictions-fantasy-points-by-position-age-bayesian3
